On Secure Delegation of SampBQP with a Classical Client

### 2020-03-31 preliminaries.tex
Get ready for next round of feedbacks
Start implementing suggestions from discussion

Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit. Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices. We use $H\geq0$ to denote $H$ being positive semidefinite. Let $\lambda(H)$ be the smallest eigenvalue of $H$. The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$. For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$. For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.

@@

De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
There are many formulations; we use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
\begin{thm}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
	where $\Lambda_i$ are quantum-classical channels.
\end{thm}

>>>>

Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit. Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices. We use $H\geq0$ to denote $H$ being positive semidefinite. Let $\lambda(H)$ be the smallest eigenvalue of $H$. The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$. For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$. For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
We write $T(\rho_1, \rho_2)=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$. $\forall \rho_1, \rho_2\in\cB^{\otimes N}$ we have $T(\rho_1, \rho_2)\leq\sqrt{1-F(\rho_1, \rho_2)}$.

@@

De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
\begin{thm}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}
	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
	\leq\sqrt{\frac{2l^2s}{k-l}}$$
	where $\Lambda_i$ are quantum-classical channels.
\end{thm}

### 2020-03-31 qpip.tex
Start implementing suggestions from discussion

\Ethan{Again, look at other papers...}

\Ethan{get style from pg 22 on other paper}

\Ethan{Also see 102, p2, 5}

\Ethan{201 p12 p23 two different styles of protocol-writing}

\Ethan{106 p31}

@@

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for the computation $C(x)$ with error parameter $\varepsilon$}
	\label{ProtoQPIP1}

@@

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ \Ethan{TODO Define this} only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	Note that the ground state has $\abs{A}=n+T+\frac{T}{\varepsilon}$ qubits.
	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
	That is, \Ethan{type out ``there exists" if in sentence} $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

@@

	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$: \Ethan{Wording issue; make it obvious I'm defining $p_j$}
	$$J=\set{j\in\bbN|p_j<\frac{1}{2}-2\kappa}$$

	\Ethan{Definition of $J$ is extraneous; just cut into two cases.}

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

>>>>

\Ethan{Actual technical part starts here}

@@

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the computation $C(x)$ with error parameter $\varepsilon$}
	\label{ProtoQPIP1}

@@

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

@@

	Let $p_j$ be the probability that $\cVGS(\rho_j)=acc$. Now we seperate the $\rho_j$ terms into two categories based on $p_j$.

	First suppose $p_j<\frac{1}{2}-2\kappa$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$
